---
title: "OpenStreetMap Integration: Actual Enrollment Analysis"
format:
  html:
    embed-resources: true
    toc: true
    toc-location: left
    theme: cosmo
    code-fold: true
lang: en
---

<style>
/* Fix z-index issue for DataTables filter dropdowns */
.dataTables_wrapper .dataTables_filter input,
.dataTables_wrapper .dataTables_length select,
div.dataTables_wrapper div.dataTables_filter input,
div.dataTables_wrapper div.dataTables_length select {
  z-index: 1000 !important;
  position: relative;
}

/* Fix for filter dropdowns appearing behind table */
thead input,
thead select {
  z-index: 1000 !important;
  position: relative;
}

/* Ensure dropdown menus appear on top */
.dataTables_scrollHead {
  z-index: 999 !important;
}

.dataTables_scrollBody {
  z-index: 1 !important;
}

/* Fix for select2 dropdowns if used */
.select2-container {
  z-index: 10000 !important;
}

.select2-dropdown {
  z-index: 10001 !important;
}

/* General fix for filter row */
.dataTables_scrollHeadInner table thead tr:first-child {
  z-index: 1000 !important;
  position: relative;
}

/* Ensure filter inputs are clickable and visible */
table.dataTable thead .sorting:before,
table.dataTable thead .sorting_asc:before,
table.dataTable thead .sorting_desc:before {
  z-index: 1 !important;
}

/* Fix for the filter input cells */
table.dataTable thead tr:first-child th {
  z-index: 1000 !important;
  position: relative;
  background: white;
}

/* Ensure the filter inputs have proper stacking */
table.dataTable thead input[type="search"] {
  z-index: 1001 !important;
  position: relative;
  background: white;
}

/* Force white text for TOTAL row in contingency table */
table.kable-table tbody tr:last-child td {
  color: white !important;
  background-color: #2c3e50 !important;
  font-weight: bold !important;
}

</style>

### OpenStreetMap Integration for Competitive Analysis - Actual Enrollment Data

This document focuses specifically on OpenStreetMap integration and advanced web mapping techniques for UAI's competitive analysis using actual enrollment data (MATRICULADOS, EGRESADOS) without filtered career restrictions.

**OpenStreetMap Features:**
- 🗺️ **Custom OpenStreetMap Tiles** with multiple providers
- 🌐 **Advanced Leaflet Integration** with custom controls
- 📊 **Real-time Data Overlays** on OpenStreetMap base layers
- 🎯 **Professional Web Mapping** with responsive design
- 📱 **Mobile-optimized Maps** with touch interactions

```{r setup, include=FALSE, message=FALSE, warning=FALSE}
# Load specialized mapping libraries
library(tidyverse)
library(leaflet)
library(leaflet.extras)
library(leaflet.providers)
library(DT)
library(reactable)

# Using standard leaflet.extras search functionality
library(RColorBrewer)
library(readr)
library(plotly)
library(classInt)
library(viridis)
library(htmlwidgets)
library(cluster)
library(factoextra)
library(kableExtra)
# library(webshot)  # Optional package

# Options for dynamic tables
options(DT.options = list(pageLength = 10, language = list(url = '//cdn.datatables.net/plug-ins/1.10.19/i18n/English.json')))
```

### 1. Data Preparation for OpenStreetMap Integration

```{r OSM_Data_Preparation, message=FALSE, warning=FALSE}
# Load and prepare data for OpenStreetMap integration
# Now using the new comprehensive CSV with both career and university clusters
# Note: File has mixed decimal separators - most columns use comma, coordinates use period
datos_raw <- read_delim("Resumen_colegios_clusters.csv", 
                        delim = ";",
                        col_types = cols(.default = "c"))  # Read everything as character first

# Convert columns properly with correct decimal separators
datos <- datos_raw %>%
  mutate(
    # Coordinates use PERIOD as decimal separator
    LATITUD = as.numeric(LATITUD),
    LONGITUD = as.numeric(LONGITUD),
    
    # Convert specific numeric columns with COMMA as decimal separator
    RBD = as.numeric(RBD),
    REGION_RBD = as.numeric(REGION_RBD),
    MATRICULADOS = as.numeric(gsub(",", ".", MATRICULADOS)),
    POSTULANTES = as.numeric(gsub(",", ".", POSTULANTES)),
    POSTULANTES_UAI = as.numeric(gsub(",", ".", POSTULANTES_UAI)),
    MATRICULADOS_UAI = as.numeric(gsub(",", ".", MATRICULADOS_UAI)),
    POST_COMPETENCIA1 = as.numeric(gsub(",", ".", POST_COMPETENCIA1)),
    POST_COMPETENCIA2 = as.numeric(gsub(",", ".", POST_COMPETENCIA2)),
    MATRI_COMPETENCIA1 = as.numeric(gsub(",", ".", MATRI_COMPETENCIA1)),
    MATRI_COMPETENCIA2 = as.numeric(gsub(",", ".", MATRI_COMPETENCIA2)),
    # Others category (unfiltered)
    MATRI_OTHERS = as.numeric(gsub(",", ".", MATRI_OTHERS)),
    POST_OTHERS = as.numeric(gsub(",", ".", POST_OTHERS)),
    # Filtered career data
    MATRI_UAI_FILTRADO = as.numeric(gsub(",", ".", MATRI_UAI_FILTRADO)),
    POST_UAI_FILTRADO = as.numeric(gsub(",", ".", POST_UAI_FILTRADO)),
    MATRI_COMPT1_FILTRADO = as.numeric(gsub(",", ".", MATRI_COMPT1_FILTRADO)),
    POST_COMPT1_FILTRADO = as.numeric(gsub(",", ".", POST_COMPT1_FILTRADO)),
    MATRI_COMPT2_FILTRADO = as.numeric(gsub(",", ".", MATRI_COMPT2_FILTRADO)),
    POST_COMPT2_FILTRADO = as.numeric(gsub(",", ".", POST_COMPT2_FILTRADO)),
    PTJE_PROM = as.numeric(gsub(",", ".", PTJE_PROM)),
    cluster_num = as.numeric(cluster_num),
    CLUSTER_UNIVERSIDAD_NUM = as.numeric(CLUSTER_UNIVERSIDAD_NUM)
  )

# Prepare data with OpenStreetMap-optimized structure - Using only actual enrollment data
datos_osm <- datos %>%
  mutate(
    # Ensure numeric conversion for actual enrollment data
    POSTULANTES_UAI = as.numeric(POSTULANTES_UAI),
    MATRICULADOS_UAI = as.numeric(MATRICULADOS_UAI),
    MATRI_COMPETENCIA_1 = as.numeric(MATRI_COMPETENCIA1),
    MATRI_COMPETENCIA_2 = as.numeric(MATRI_COMPETENCIA2),
    POSTULANTES_COMPETENCIA_1 = as.numeric(POST_COMPETENCIA1),
    POSTULANTES_COMPETENCIA_2 = as.numeric(POST_COMPETENCIA2),
    PTJE_PROM = as.numeric(PTJE_PROM),
    
    # Use actual enrollment data (no filtered careers)
    POST_UAI_ACTUAL = as.numeric(POSTULANTES_UAI),
    MATRI_UAI_ACTUAL = as.numeric(MATRICULADOS_UAI),
    POST_COMP1_ACTUAL = as.numeric(POST_COMPETENCIA1),
    POST_COMP2_ACTUAL = as.numeric(POST_COMPETENCIA2),
    MATRI_COMP1_ACTUAL = as.numeric(MATRI_COMPETENCIA1),
    MATRI_COMP2_ACTUAL = as.numeric(MATRI_COMPETENCIA2),
    POST_OTHERS_ACTUAL = as.numeric(POST_OTHERS),
    MATRI_OTHERS_ACTUAL = as.numeric(MATRI_OTHERS),
    
    # Competitive metrics - Using ACTUAL ENROLLMENT data (including Others)
    TOTAL_MARKET_MATRI = MATRICULADOS_UAI + MATRI_COMPETENCIA1 + MATRI_COMPETENCIA2 + MATRI_OTHERS,
    
    # Market Share Analysis - Using actual enrollment data (including Others)
    MARKET_SHARE_UAI_MATRI = if_else(TOTAL_MARKET_MATRI > 0, (MATRICULADOS_UAI / TOTAL_MARKET_MATRI) * 100, 0),
    MARKET_SHARE_COMP1_MATRI = if_else(TOTAL_MARKET_MATRI > 0, (MATRI_COMPETENCIA1 / TOTAL_MARKET_MATRI) * 100, 0),
    MARKET_SHARE_COMP2_MATRI = if_else(TOTAL_MARKET_MATRI > 0, (MATRI_COMPETENCIA2 / TOTAL_MARKET_MATRI) * 100, 0),
    MARKET_SHARE_OTHERS_MATRI = if_else(TOTAL_MARKET_MATRI > 0, (MATRI_OTHERS / TOTAL_MARKET_MATRI) * 100, 0),
    
    # Inverse Lift Logic: UAI as numerator (bigger is better) - Using actual data
    LIFT_UAI_vs_COMP1 = if_else(MATRI_COMPETENCIA1 > 0, MATRICULADOS_UAI / MATRI_COMPETENCIA1, 0),
    LIFT_UAI_vs_COMP2 = if_else(MATRI_COMPETENCIA2 > 0, MATRICULADOS_UAI / MATRI_COMPETENCIA2, 0),
    
    # Combined competitive position
    COMPETITIVE_POSITION = case_when(
      LIFT_UAI_vs_COMP1 >= 2 & LIFT_UAI_vs_COMP2 >= 2 ~ "UAI Dominant",
      LIFT_UAI_vs_COMP1 >= 1.5 | LIFT_UAI_vs_COMP2 >= 1.5 ~ "UAI Strong",
      LIFT_UAI_vs_COMP1 >= 1 | LIFT_UAI_vs_COMP2 >= 1 ~ "UAI Advantage",
      LIFT_UAI_vs_COMP1 >= 0.7 & LIFT_UAI_vs_COMP2 >= 0.7 ~ "Balanced",
      LIFT_UAI_vs_COMP1 >= 0.5 | LIFT_UAI_vs_COMP2 >= 0.5 ~ "Competitor Advantage",
      TRUE ~ "Competitor Dominant"
    )
  ) %>%
  # Rename for consistency - keep both career and university cluster info
  rename(CLUSTER_ID = "cluster_num") %>%
  # Map CLUSTER_CARRERA to CLUSTER_NOMBRE for backward compatibility with existing code
  mutate(CLUSTER_NOMBRE = CLUSTER_CARRERA) %>%
  # Use CLUSTER_UNIVERSIDAD directly instead of calculated COMPETITIVE_POSITION
  mutate(COMPETITIVE_CATEGORY = ifelse(is.na(CLUSTER_UNIVERSIDAD) | CLUSTER_UNIVERSIDAD == "", "No Cluster", CLUSTER_UNIVERSIDAD))

# Filter schools for OpenStreetMap visualization - Using actual enrollment data
# Keep all schools with valid cluster assignments (career clusters 1-6)
datos_osm <- datos_osm %>%
  filter(!is.na(CLUSTER_ID) & CLUSTER_ID %in% 1:6)
  # NOTE: CLUSTER_CARRERA already exists in the data with meaningful names!
  # CLUSTER_UNIVERSIDAD contains university cluster assignments (1-8)

# Filter for OpenStreetMap visualization - Using actual enrollment data
datos_osm_clean <- datos_osm %>%
  filter(POST_UAI_ACTUAL > 0 | MATRI_UAI_ACTUAL > 0 | 
         POST_COMP1_ACTUAL > 0 | MATRI_COMP1_ACTUAL > 0 |
         POST_COMP2_ACTUAL > 0 | MATRI_COMP2_ACTUAL > 0 |
         POST_OTHERS_ACTUAL > 0 | MATRI_OTHERS_ACTUAL > 0) %>%
  filter(!is.na(LATITUD) & !is.na(LONGITUD) & 
         LATITUD != "" & LONGITUD != "" &
         LATITUD != "NA" & LONGITUD != "NA") %>%
  mutate(
    LATITUD = as.numeric(LATITUD),
    LONGITUD = as.numeric(LONGITUD)
  ) %>%
  filter(!is.na(LATITUD) & !is.na(LONGITUD) &
         LATITUD >= -56 & LATITUD <= -17 &  # Chile bounds
         LONGITUD >= -76 & LONGITUD <= -66) %>%
  mutate(
    # Use CLUSTER_UNIVERSIDAD directly instead of calculated COMPETITIVE_POSITION
    COMPETITIVE_CATEGORY = ifelse(is.na(CLUSTER_UNIVERSIDAD) | CLUSTER_UNIVERSIDAD == "", "No Cluster", CLUSTER_UNIVERSIDAD),
    
    # Market dominance indicators
    UAI_MARKET_DOMINANCE = case_when(
      MARKET_SHARE_UAI_MATRI >= 50 ~ "Market Leader",
      MARKET_SHARE_UAI_MATRI >= 30 ~ "Strong Position",
      MARKET_SHARE_UAI_MATRI >= 15 ~ "Moderate Position",
      MARKET_SHARE_UAI_MATRI >= 5 ~ "Weak Position",
      TRUE ~ "Minimal Presence"
    )
  )

cat("OpenStreetmap dataset prepared with", nrow(datos_osm_clean), "schools\n")
```


### University Cluster Centers Analysis (6 Final Clusters)

```{r University_Cluster_Centers, message=FALSE, warning=FALSE, echo=FALSE}
# Calculate university cluster centers using FILTERED data (normalized percentages)
university_cluster_centers <- datos_osm_clean %>%
  filter(!is.na(CLUSTER_UNIVERSIDAD) & CLUSTER_UNIVERSIDAD != "") %>%
  mutate(
    # Use FILTERED percentages and normalize them
    UAI_FILT = coalesce(as.numeric(gsub(",", ".", gsub("%", "", PCNTJE_MATRI_UAI_FILTRADO))), 0),
    COMP1_FILT = coalesce(as.numeric(gsub(",", ".", gsub("%", "", PCNTJE_COMPT1_MATRI_FILTRADO))), 0),
    COMP2_FILT = coalesce(as.numeric(gsub(",", ".", gsub("%", "", PCNTJE_COMPT2_MATRI_FILTRADO))), 0),
    OTHERS_FILT = pmax(0, 100 - UAI_FILT - COMP1_FILT - COMP2_FILT),
    SUMA_FILT = UAI_FILT + COMP1_FILT + COMP2_FILT + OTHERS_FILT
  ) %>%
  filter(SUMA_FILT > 0) %>%
  mutate(
    # Normalize to 100%
    UAI_NORM = (UAI_FILT / SUMA_FILT) * 100,
    COMP1_NORM = (COMP1_FILT / SUMA_FILT) * 100,
    COMP2_NORM = (COMP2_FILT / SUMA_FILT) * 100,
    OTHERS_NORM = (OTHERS_FILT / SUMA_FILT) * 100
  ) %>%
  group_by(CLUSTER_UNIVERSIDAD) %>%
  summarise(
    n_schools = n(),
    avg_uai_pct = round(mean(UAI_NORM, na.rm = TRUE), 2),
    avg_comp1_pct = round(mean(COMP1_NORM, na.rm = TRUE), 2),
    avg_comp2_pct = round(mean(COMP2_NORM, na.rm = TRUE), 2),
    avg_others_pct = round(mean(OTHERS_NORM, na.rm = TRUE), 2),
    suma_check = round(avg_uai_pct + avg_comp1_pct + avg_comp2_pct + avg_others_pct, 2),
    .groups = 'drop'
  ) %>%
  arrange(desc(n_schools))

cat("#### University Cluster Distribution\n\n")
university_distribution <- university_cluster_centers %>%
  select(CLUSTER_UNIVERSIDAD, n_schools) %>%
  mutate(percentage = round((n_schools / sum(n_schools)) * 100, 1)) %>%
  arrange(desc(n_schools))

university_distribution %>%
  kableExtra::kbl(
    col.names = c("University Cluster", "Number of Schools", "Percentage"),
    align = c("l", "r", "r"),
    format = "html",
    escape = FALSE
  ) %>%
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed", "responsive"),
    full_width = FALSE,
    position = "left",
    font_size = 12
  ) %>%
  row_spec(0, background = "#2c3e50", color = "white", bold = TRUE) %>%
  column_spec(1, bold = TRUE, color = "#2c3e50") %>%
  column_spec(2:3, color = "#34495e") %>%
  add_header_above(c(" " = 1, "Distribution" = 2), background = "#34495e", color = "white", bold = TRUE)

cat("\n#### University Cluster Centers (Normalized Percentages - Filtered Data)\n\n")
cat("**Note:** Percentages are normalized so UAI + COMP1 + COMP2 + OTHERS = 100%\\n")
cat("This shows the relative preference within these 4 categories using FILTERED matriculation data.\\n\\n")

university_cluster_centers %>%
  kableExtra::kbl(
    col.names = c("University Cluster", "Schools", "UAI %", "COMP1 %", "COMP2 %", "OTHERS %", "Sum Check"),
    align = c("l", "r", "r", "r", "r", "r", "r"),
    format = "html",
    escape = FALSE,
    digits = 2
  ) %>%
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed", "responsive"),
    full_width = FALSE,
    position = "left",
    font_size = 11
  ) %>%
  row_spec(0, background = "#34495e", color = "white", bold = TRUE) %>%
  column_spec(1, bold = TRUE, color = "#2c3e50") %>%
  column_spec(2, color = "#27ae60", bold = TRUE) %>%
  column_spec(3, color = "#3498db") %>%
  column_spec(4, color = "#e67e22") %>%
  column_spec(5, color = "#9b59b6") %>%
  column_spec(6, color = "#95a5a6") %>%
  column_spec(7, color = "#e74c3c", bold = TRUE) %>%
  add_header_above(c(" " = 1, "Schools" = 1, "Normalized Percentages" = 4, "Validation" = 1), 
                   background = "#2c3e50", color = "white", bold = TRUE)
```

### Career Cluster Analysis Summary

```{r Cluster_Statistics_Summary, message=FALSE, warning=FALSE, echo=FALSE}
# Calculate cluster statistics using MATRICULATION data (same as used for clustering)
cluster_stats <- datos_osm_clean %>%
  filter(!is.na(CLUSTER_NOMBRE) & CLUSTER_NOMBRE != "") %>%
  mutate(
    # Convert percentages to numeric - USE MATRICULATION DATA (same as clustering)
    COMERCIAL_RAW = coalesce(as.numeric(gsub(",", ".", gsub("%", "", PCNTJE_COMERCIAL_MATRI))), 0),
    DERECHO_RAW = coalesce(as.numeric(gsub(",", ".", gsub("%", "", PCNTJE_DERECHO_MATRI))), 0),
    CIVIL_RAW = coalesce(as.numeric(gsub(",", ".", gsub("%", "", PCNTJE_ING_CIVIL_MATRI))), 0),
    PSICOLOGIA_RAW = coalesce(as.numeric(gsub(",", ".", gsub("%", "", PCNTJE_PSICOLOGIA_MATRI))), 0),
    PERIODISMO_RAW = coalesce(as.numeric(gsub(",", ".", gsub("%", "", PCNTJE_PERIODISMO_MATRI))), 0),
    # Calculate sum of strategic careers
    SUMA_ESTRATEGICAS = COMERCIAL_RAW + DERECHO_RAW + CIVIL_RAW + PSICOLOGIA_RAW + PERIODISMO_RAW
  ) %>%
  # Only include schools with at least one strategic career
  filter(SUMA_ESTRATEGICAS > 0) %>%
  # Normalize to 100% (same as clustering process)
  mutate(
    COMERCIAL_NORM = (COMERCIAL_RAW / SUMA_ESTRATEGICAS) * 100,
    DERECHO_NORM = (DERECHO_RAW / SUMA_ESTRATEGICAS) * 100,
    CIVIL_NORM = (CIVIL_RAW / SUMA_ESTRATEGICAS) * 100,
    PSICOLOGIA_NORM = (PSICOLOGIA_RAW / SUMA_ESTRATEGICAS) * 100,
    PERIODISMO_NORM = (PERIODISMO_RAW / SUMA_ESTRATEGICAS) * 100
  ) %>%
  group_by(CLUSTER_NOMBRE) %>%
  summarise(
    n_schools = n(),
    # Average normalized percentages (sum to 100% per cluster)
    avg_commercial = round(mean(COMERCIAL_NORM, na.rm = TRUE), 2),
    avg_civil = round(mean(CIVIL_NORM, na.rm = TRUE), 2),
    avg_law = round(mean(DERECHO_NORM, na.rm = TRUE), 2),
    avg_psychology = round(mean(PSICOLOGIA_NORM, na.rm = TRUE), 2),
    avg_journalism = round(mean(PERIODISMO_NORM, na.rm = TRUE), 2),
    # Check that they sum to 100%
    suma_check = round(avg_commercial + avg_civil + avg_law + avg_psychology + avg_journalism, 2),
    .groups = 'drop'
  ) %>%
  arrange(desc(n_schools))

# Create distribution summary
cluster_distribution <- datos_osm_clean %>%
  filter(!is.na(CLUSTER_NOMBRE) & CLUSTER_NOMBRE != "") %>%
  count(CLUSTER_NOMBRE, name = "count") %>%
  mutate(percentage = round((count / sum(count)) * 100, 1)) %>%
  arrange(desc(count))

cat("#### Cluster Distribution\n\n")
cluster_distribution %>%
  kableExtra::kbl(
                   col.names = c("Cluster Name", "Number of Schools", "Percentage"),
    align = c("l", "r", "r"),
    format = "html",
    escape = FALSE
  ) %>%
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed", "responsive"),
    full_width = FALSE,
    position = "left",
    font_size = 12
  ) %>%
  row_spec(0, background = "#2c3e50", color = "white", bold = TRUE) %>%
  column_spec(1, bold = TRUE, color = "#2c3e50") %>%
  column_spec(2:3, color = "#34495e") %>%
  add_header_above(c(" " = 1, "Distribution" = 2), background = "#34495e", color = "white", bold = TRUE)

cat("\n#### Cluster Characteristics (Normalized Percentages - Sum to 100%)\n\n")
cat("Note: Percentages are normalized across the 5 strategic careers so they sum to 100%.\n")
cat("This shows the relative preference within these careers (MATRICULATION data, same as used for clustering).\n\n")
cluster_stats %>%
  select(-suma_check) %>%
  kableExtra::kbl(
                   col.names = c("Cluster Name", "Schools", "Commercial %", "Civil %", "Law %", "Psychology %", "Journalism %"),
                   align = c("l", "r", "r", "r", "r", "r", "r"),
    format = "html",
    escape = FALSE,
    digits = 2
  ) %>%
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed", "responsive"),
    full_width = FALSE,
    position = "left",
    font_size = 11
  ) %>%
  row_spec(0, background = "#34495e", color = "white", bold = TRUE) %>%
  column_spec(1, bold = TRUE, color = "#2c3e50") %>%
  column_spec(2, color = "#27ae60", bold = TRUE) %>%
  column_spec(3, color = "#9b59b6") %>%
  column_spec(4, color = "#e74c3c") %>%
  column_spec(5, color = "#f39c12") %>%
  column_spec(6, color = "#1abc9c") %>%
  column_spec(7, color = "#3498db") %>%
  add_header_above(c(" " = 1, "Schools" = 1, "Career Distribution (Normalized %)" = 5), 
                   background = "#2c3e50", color = "white", bold = TRUE)

```

### Contingency Table: University Cluster × Career Dominant

```{r Contingency_Table, message=FALSE, warning=FALSE, echo=FALSE}
# Create contingency table: Cluster Universidad × Carrera Dominante
datos_con_carrera_dom <- datos_osm_clean %>%
  filter(!is.na(CLUSTER_UNIVERSIDAD) & CLUSTER_UNIVERSIDAD != '' &
         !is.na(CLUSTER_CARRERA) & CLUSTER_CARRERA != '' & CLUSTER_CARRERA != 'Other') %>%
  mutate(
    COMERCIAL = coalesce(as.numeric(gsub(',', '.', gsub('%', '', PCNTJE_COMERCIAL_MATRI))), 0),
    ING_CIVIL = coalesce(as.numeric(gsub(',', '.', gsub('%', '', PCNTJE_ING_CIVIL_MATRI))), 0),
    DERECHO = coalesce(as.numeric(gsub(',', '.', gsub('%', '', PCNTJE_DERECHO_MATRI))), 0),
    PSICOLOGIA = coalesce(as.numeric(gsub(',', '.', gsub('%', '', PCNTJE_PSICOLOGIA_MATRI))), 0),
    PERIODISMO = coalesce(as.numeric(gsub(',', '.', gsub('%', '', PCNTJE_PERIODISMO_MATRI))), 0),
    MAX_PCT = pmax(COMERCIAL, ING_CIVIL, DERECHO, PSICOLOGIA, PERIODISMO),
    CARRERA_DOMINANTE = case_when(
      abs(MAX_PCT - COMERCIAL) < 0.01 ~ 'Comercial',
      abs(MAX_PCT - ING_CIVIL) < 0.01 ~ 'Ing_Civil',
      abs(MAX_PCT - DERECHO) < 0.01 ~ 'Derecho',
      abs(MAX_PCT - PSICOLOGIA) < 0.01 ~ 'Psicologia',
      abs(MAX_PCT - PERIODISMO) < 0.01 ~ 'Periodismo',
      TRUE ~ 'Otra'
    )
  )

# Count by combination
conteos <- datos_con_carrera_dom %>%
  count(CLUSTER_UNIVERSIDAD, CARRERA_DOMINANTE)

# Convert to contingency table
library(data.table)
conteos_dt <- as.data.table(conteos)
tabla_n <- dcast(conteos_dt, 
                 CLUSTER_UNIVERSIDAD ~ CARRERA_DOMINANTE, 
                 value.var = 'n', 
                 fill = 0)

# Calculate % of total global
total_colegios <- sum(conteos$n)
tabla_pct <- tabla_n %>%
  mutate(across(-CLUSTER_UNIVERSIDAD, ~ round((.x / total_colegios) * 100, 2))) %>%
  mutate(TOTAL_FILA = round(rowSums(select(., -CLUSTER_UNIVERSIDAD)), 2))

# Add column totals
totales_col <- tabla_pct %>%
  summarise(across(-CLUSTER_UNIVERSIDAD, sum)) %>%
  mutate(CLUSTER_UNIVERSIDAD = 'TOTAL')

tabla_pct <- bind_rows(tabla_pct, totales_col)

cat("#### Contingency Table: University Cluster × Career Dominant\n\n")
cat("**Note:** Each cell shows the % of the TOTAL number of schools with that combination.\\n")
cat("All cells together represent 100% of the school universe.\\n\\n")

tabla_pct %>%
  kableExtra::kbl(
    col.names = c("University Cluster", "Comercial", "Derecho", "Ing_Civil", "Periodismo", "Psicologia", "TOTAL"),
    align = c("l", "r", "r", "r", "r", "r", "r"),
    format = "html",
    escape = FALSE,
    digits = 2
  ) %>%
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed", "responsive"),
    full_width = FALSE,
    position = "left",
    font_size = 11
  ) %>%
  row_spec(0, background = "#34495e", color = "white", bold = TRUE) %>%
  column_spec(1, bold = TRUE, color = "#2c3e50") %>%
  column_spec(2:6, color = "#34495e") %>%
  column_spec(7, color = "#e74c3c", bold = TRUE) %>%
  # Apply white text to TOTAL row - this must be last to override column colors
  row_spec(which(tabla_pct$CLUSTER_UNIVERSIDAD == "TOTAL"), 
           background = "#2c3e50", 
           color = "white", 
           bold = TRUE,
           extra_css = "td, td:nth-child(1), td:nth-child(2), td:nth-child(3), td:nth-child(4), td:nth-child(5), td:nth-child(6), td:nth-child(7) { color: white !important; background-color: #2c3e50 !important; }") %>%
  add_header_above(c("University Cluster" = 1, "Career Dominant (%)" = 5, "Total" = 1), 
                   background = "#2c3e50", color = "white", bold = TRUE) %>%
  footnote(
    general = "Each cell shows the % of the TOTAL number of schools. All cells together represent 100% of the school universe.",
    general_title = "Note:",
    footnote_as_chunk = TRUE
  )
```

### Helper Function: Add Slider Filters

```{r Add_Filter_Controls, message=FALSE, warning=FALSE}
# Function to add filter controls with sliders to any map
add_filter_controls <- function(map) {
  htmlwidgets::onRender(map, "
    function(el, x) {
      var map = this;
      
      // Store all markers for filtering (with their groups and layer groups)
      var allMarkers = [];
      var markerToLayerGroup = {}; // Track which LayerGroup each marker belongs to
      
      // Function to collect markers from all sources (map and layer groups)
      function collectMarkers() {
        allMarkers = [];
        markerToLayerGroup = {};
        
        // Collect markers from the map directly
        map.eachLayer(function(layer) {
          if (layer instanceof L.CircleMarker && layer.options.popup) {
            allMarkers.push(layer);
            markerToLayerGroup[layer._leaflet_id] = null; // Directly on map
          }
        });
        
        // Also collect markers from all layer groups (even if not visible)
        map.eachLayer(function(layer) {
          if (layer instanceof L.LayerGroup) {
            layer.eachLayer(function(subLayer) {
              if (subLayer instanceof L.CircleMarker && subLayer.options.popup) {
                // Check if we already have this marker
                var alreadyFound = false;
                for (var i = 0; i < allMarkers.length; i++) {
                  if (allMarkers[i]._leaflet_id === subLayer._leaflet_id) {
                    alreadyFound = true;
                    // Update the layer group reference
                    markerToLayerGroup[subLayer._leaflet_id] = layer;
                    break;
                  }
                }
                if (!alreadyFound) {
                  allMarkers.push(subLayer);
                  markerToLayerGroup[subLayer._leaflet_id] = layer;
                }
              }
            });
          }
        });
        map.eachLayer(function(layer) {
          if (layer instanceof L.CircleMarker && layer.options.popup) {
            allMarkers.push(layer);
          }
        });
      }
      
      // Collect markers initially
      collectMarkers();
      
      // Find max value for Total Students slider
      var maxTotal = 0;
      allMarkers.forEach(function(marker) {
        var popupContent = marker.options.popup;
        // Match Total Students with or without (5 Key Careers) prefix  
        var totalMatch = popupContent.match(/Total Students[^:]*:<\\/strong>\\s*([0-9,]+)/);
        
        if (totalMatch) {
          var totalVal = parseInt(totalMatch[1].toString().replace(/,/g, '')) || 0;
          if (totalVal > maxTotal) maxTotal = totalVal;
        }
      });
      
      // Create custom control panel
      var controlPanel = L.control({position: 'topright'});
      
      controlPanel.onAdd = function(map) {
        var div = L.DomUtil.create('div', 'filter-control-panel');
        div.style.cssText = 'background: white; padding: 15px; border-radius: 8px; box-shadow: 0 2px 10px rgba(0,0,0,0.3); min-width: 280px; z-index: 1000;';
        
        // Title
        var title = document.createElement('h4');
        title.textContent = 'Total Students';
        title.style.cssText = 'margin: 0 0 15px 0; font-size: 16px; color: #333;';
        div.appendChild(title);
        
        // Total Students Filter
        var totalLabel = document.createElement('label');
        totalLabel.textContent = 'Total Students (min):';
        totalLabel.style.cssText = 'display: block; margin-bottom: 5px; font-size: 12px; font-weight: bold; color: #555;';
        div.appendChild(totalLabel);
        
        var totalSlider = document.createElement('input');
        totalSlider.type = 'range';
        totalSlider.min = '0';
        totalSlider.max = String(Math.min(maxTotal, 500));
        totalSlider.value = '0';
        totalSlider.step = '10';
        totalSlider.style.cssText = 'width: 100%; margin-bottom: 10px;';
        div.appendChild(totalSlider);
        
        var totalValue = document.createElement('span');
        totalValue.textContent = '0';
        totalValue.style.cssText = 'display: block; text-align: center; font-size: 14px; font-weight: bold; color: #667eea; margin-bottom: 10px;';
        div.appendChild(totalValue);
        
        // Update value displays
        uaiSlider.addEventListener('input', function() {
          uaiValue.textContent = this.value;
        });
        
        totalSlider.addEventListener('input', function() {
          totalValue.textContent = this.value;
        });
        
        // Filter function
        function filterMarkers() {
          var uaiMin = parseInt(uaiSlider.value);
          var totalMin = parseInt(totalSlider.value);
          var visibleCount = 0;
          
          allMarkers.forEach(function(marker) {
            // Extract data from popup HTML
            var popupContent = marker.options.popup;
            var uaiMatch = popupContent.match(/UAI.*?Enrolled.*?strong>Enrolled:<\\/strong>[^>]*>([^<]+)</);
            var totalMatch = popupContent.match(/Total Students:<\\/strong>[^>]*>([^<]+)/);
            
            var uaiVal = uaiMatch ? parseInt(uaiMatch[1].replace(/,/g, '')) || 0 : 0;
            var totalVal = totalMatch ? parseInt(totalMatch[1].replace(/,/g, '')) || 0 : 0;
            
            if (uaiVal >= uaiMin && totalVal >= totalMin) {
              if (!map.hasLayer(marker)) {
                marker.addTo(map);
              }
              visibleCount++;
            } else {
              if (map.hasLayer(marker)) {
                marker.remove();
              }
            }
          });
          
          // Update title with count
          title.textContent = 'Total Students (' + visibleCount + ' visible)';
        }
        
        // Bind filter to sliders
        uaiSlider.addEventListener('input', filterMarkers);
        totalSlider.addEventListener('input', filterMarkers);
        
        L.DomEvent.disableClickPropagation(div);
        L.DomEvent.disableScrollPropagation(div);
        
        return div;
      };
      
      map.addControl(controlPanel);
    }
  ")
  
  return(map)
}
```

### 2. OpenStreetMap Base Layers and Custom Tiles

```{r OSM_Base_Layers, message=FALSE, warning=FALSE}
# Create comprehensive OpenStreetMap integration
osm_comprehensive_map <- leaflet() %>%
  # Add multiple OpenStreetMap tile layers
  addProviderTiles(providers$OpenStreetMap, group = "OpenStreetMap Standard") %>%
  addProviderTiles(providers$OpenStreetMap.DE, group = "OpenStreetMap DE") %>%
  addProviderTiles(providers$OpenStreetMap.France, group = "OpenStreetMap France") %>%
  addProviderTiles(providers$OpenStreetMap.HOT, group = "OpenStreetMap HOT") %>%
  
  # Add alternative base layers for comparison
  addProviderTiles(providers$CartoDB.Positron, group = "CartoDB Light") %>%
  addProviderTiles(providers$CartoDB.DarkMatter, group = "CartoDB Dark") %>%
  addProviderTiles(providers$Esri.WorldStreetMap, group = "Esri Street") %>%
  addProviderTiles(providers$Esri.WorldImagery, group = "Satellite") %>%
  addProviderTiles(providers$CartoDB.Positron, group = "Stamen Toner") %>%
  addProviderTiles(providers$CartoDB.Positron, group = "Stamen Terrain") %>%
  
  # Add fixed university markers (always visible) - one marker for each individual university
  # UAI Group - Blue color (#0000FF)
  addCircleMarkers(
    lng = -70.518, lat = -33.486,  # UAI Santiago - Campus Peñalolén
    radius = 12,
    color = "#0000FF",
    fillColor = "#0000FF",
    fillOpacity = 1,
    weight = 3,
    stroke = TRUE,
    popup = "<div style='font-size: 14px; width: 250px;'><div style='background: linear-gradient(135deg, #0000FF 0%, #2980b9 100%); color: white; padding: 12px; border-radius: 8px;'><h3 style='margin: 0; font-size: 18px;'>🏛️ UAI</h3><p style='margin: 5px 0 0 0; font-size: 12px; opacity: 0.9;'>Universidad Adolfo Ibáñez<br>Campus Peñalolén</p></div></div>"
  ) %>%
  addCircleMarkers(
    lng = -71.554162, lat = -33.011707,  # UAI Viña del Mar
    radius = 12,
    color = "#0000FF",
    fillColor = "#0000FF",
    fillOpacity = 1,
    weight = 3,
    stroke = TRUE,
    popup = "<div style='font-size: 14px; width: 250px;'><div style='background: linear-gradient(135deg, #0000FF 0%, #2980b9 100%); color: white; padding: 12px; border-radius: 8px;'><h3 style='margin: 0; font-size: 18px;'>🏛️ UAI</h3><p style='margin: 5px 0 0 0; font-size: 12px; opacity: 0.9;'>Universidad Adolfo Ibáñez<br>Campus Viña del Mar</p></div></div>"
  ) %>%
  # COMP1 Group - Green color (#00FF00)
  addCircleMarkers(
    lng = -70.6406, lat = -33.4411,  # PUC - 33°26′28″S 70°38′26″O
    radius = 12,
    color = "#00FF00",
    fillColor = "#00FF00",
    fillOpacity = 1,
    weight = 3,
    stroke = TRUE,
    popup = "<div style='font-size: 14px; width: 250px;'><div style='background: linear-gradient(135deg, #00FF00 0%, #27ae60 100%); color: white; padding: 12px; border-radius: 8px;'><h3 style='margin: 0; font-size: 18px;'>🏛️ COMP1</h3><p style='margin: 5px 0 0 0; font-size: 12px; opacity: 0.9;'>Pontificia Universidad Católica<br>Campus San Joaquín</p></div></div>"
  ) %>%
  addCircleMarkers(
    lng = -70.6633, lat = -33.4575,  # U. de Chile - 33°27′27″S 70°39′48″O
    radius = 12,
    color = "#00FF00",
    fillColor = "#00FF00",
    fillOpacity = 1,
    weight = 3,
    stroke = TRUE,
    popup = "<div style='font-size: 14px; width: 250px;'><div style='background: linear-gradient(135deg, #00FF00 0%, #27ae60 100%); color: white; padding: 12px; border-radius: 8px;'><h3 style='margin: 0; font-size: 18px;'>🏛️ COMP1</h3><p style='margin: 5px 0 0 0; font-size: 12px; opacity: 0.9;'>Universidad de Chile<br>Campus Beauchef</p></div></div>"
  ) %>%
  addCircleMarkers(
    lng = -71.595, lat = -33.035,  # USM - 33°02′06″S 71°35′42″O
    radius = 12,
    color = "#00FF00",
    fillColor = "#00FF00",
    fillOpacity = 1,
    weight = 3,
    stroke = TRUE,
    popup = "<div style='font-size: 14px; width: 250px;'><div style='background: linear-gradient(135deg, #00FF00 0%, #27ae60 100%); color: white; padding: 12px; border-radius: 8px;'><h3 style='margin: 0; font-size: 18px;'>🏛️ COMP1</h3><p style='margin: 5px 0 0 0; font-size: 12px; opacity: 0.9;'>Universidad Santa María<br>Valparaíso</p></div></div>"
  ) %>%
  addCircleMarkers(
    lng = -71.6056, lat = -33.0447,  # PUCV - 33°02′41″S 71°36′20″O
    radius = 12,
    color = "#00FF00",
    fillColor = "#00FF00",
    fillOpacity = 1,
    weight = 3,
    stroke = TRUE,
    popup = "<div style='font-size: 14px; width: 250px;'><div style='background: linear-gradient(135deg, #00FF00 0%, #27ae60 100%); color: white; padding: 12px; border-radius: 8px;'><h3 style='margin: 0; font-size: 18px;'>🏛️ COMP1</h3><p style='margin: 5px 0 0 0; font-size: 12px; opacity: 0.9;'>Pontificia Universidad Católica de Valparaíso<br>Valparaíso</p></div></div>"
  ) %>%
  addCircleMarkers(
    lng = -70.682766, lat = -33.448942,  # USACH - 33°26′56″S 70°40′58″O
    radius = 12,
    color = "#00FF00",
    fillColor = "#00FF00",
    fillOpacity = 1,
    weight = 3,
    stroke = TRUE,
    popup = "<div style='font-size: 14px; width: 250px;'><div style='background: linear-gradient(135deg, #00FF00 0%, #27ae60 100%); color: white; padding: 12px; border-radius: 8px;'><h3 style='margin: 0; font-size: 18px;'>🏛️ COMP1</h3><p style='margin: 5px 0 0 0; font-size: 12px; opacity: 0.9;'>Universidad de Santiago de Chile<br>Campus Santiago</p></div></div>"
  ) %>%
  # COMP2 Group - Magenta color (#FF00FF)
  addCircleMarkers(
    lng = -70.5011, lat = -33.3917,  # UDD - 33°23′30″S 70°30′04″O
    radius = 12,
    color = "#FF00FF",
    fillColor = "#FF00FF",
    fillOpacity = 1,
    weight = 3,
    stroke = TRUE,
    popup = "<div style='font-size: 14px; width: 250px;'><div style='background: linear-gradient(135deg, #FF00FF 0%, #9b59b6 100%); color: white; padding: 12px; border-radius: 8px;'><h3 style='margin: 0; font-size: 18px;'>🏛️ COMP2</h3><p style='margin: 5px 0 0 0; font-size: 12px; opacity: 0.9;'>Universidad del Desarrollo<br>Campus Las Condes</p></div></div>"
  ) %>%
  addCircleMarkers(
    lng = -70.507468, lat = -33.404007,  # U. de los Andes - UANDES
    radius = 12,
    color = "#FF00FF",
    fillColor = "#FF00FF",
    fillOpacity = 1,
    weight = 3,
    stroke = TRUE,
    popup = "<div style='font-size: 14px; width: 250px;'><div style='background: linear-gradient(135deg, #FF00FF 0%, #9b59b6 100%); color: white; padding: 12px; border-radius: 8px;'><h3 style='margin: 0; font-size: 18px;'>🏛️ COMP2</h3><p style='margin: 5px 0 0 0; font-size: 12px; opacity: 0.9;'>Universidad de los Andes<br>Campus San Carlos</p></div></div>"
  ) %>%
  addCircleMarkers(
    lng = -71.5423, lat = -33.0337,  # UNAB - 33°02′01.4″S 71°32′32.1″O
    radius = 12,
    color = "#FF00FF",
    fillColor = "#FF00FF",
    fillOpacity = 1,
    weight = 3,
    stroke = TRUE,
    popup = "<div style='font-size: 14px; width: 250px;'><div style='background: linear-gradient(135deg, #FF00FF 0%, #9b59b6 100%); color: white; padding: 12px; border-radius: 8px;'><h3 style='margin: 0; font-size: 18px;'>🏛️ COMP2</h3><p style='margin: 5px 0 0 0; font-size: 12px; opacity: 0.9;'>Universidad Andrés Bello<br>Campus Viña del Mar</p></div></div>"
  ) %>%
  
  # Add competitive analysis layer - Enhanced with COMPT1 and inverse lift logic
  addCircleMarkers(
    data = datos_osm_clean,
    lng = ~LONGITUD, lat = ~LATITUD,
    color = ~case_when(
      CLUSTER_UNIVERSIDAD == "OTHERS_COMP1_LOW" ~ "#FF0000",      # Rojo puro
      CLUSTER_UNIVERSIDAD == "UAI" ~ "#0000FF",                   # Azul puro
      CLUSTER_UNIVERSIDAD == "COMP1" ~ "#00FF00",                 # Verde puro
      CLUSTER_UNIVERSIDAD == "COMP1_COMP2" ~ "#FF00FF",           # Magenta
      CLUSTER_UNIVERSIDAD == "UAI2" ~ "#FFA500",                  # Naranja
      CLUSTER_UNIVERSIDAD == "Others" ~ "#9B59B6",                # Púrpura
      TRUE ~ "#2F2F2F"                                            # Gris muy oscuro
    ),
    stroke = TRUE, weight = 2, fillOpacity = 0.8,
    radius = ~case_when(
      MATRICULADOS >= 500 ~ 15,
      MATRICULADOS >= 200 ~ 12,
      MATRICULADOS >= 50 ~ 8,
      TRUE ~ 5
    ),
    popup = ~paste("<div style='font-size: 12px; width: 320px;'>",
                   "<div style='background: linear-gradient(135deg, #667eea 0%, #764ba2 100%); color: white; padding: 10px; border-radius: 8px 8px 0 0; margin: -10px -10px 10px -10px;'>",
                   "<h3 style='margin: 0; font-size: 16px;'>", NOM_RBD, "</h3>",
                   "</div>",
                   "<div style='background: #f8f9fa; padding: 10px; border-radius: 0 0 8px 8px;'>",
                   "<div style='display: flex; justify-content: space-between; margin-bottom: 10px;'>",
                   "<span style='background: ", 
                   case_when(
                     CLUSTER_UNIVERSIDAD == "OTHERS_COMP1_LOW" ~ "#FF0000",      # Rojo puro
                     CLUSTER_UNIVERSIDAD == "UAI" ~ "#0000FF",                   # Azul puro
                     CLUSTER_UNIVERSIDAD == "COMP1" ~ "#00FF00",                 # Verde puro
                     CLUSTER_UNIVERSIDAD == "COMP1_COMP2" ~ "#FF00FF",           # Magenta
                     CLUSTER_UNIVERSIDAD == "UAI2" ~ "#FFA500",                  # Naranja
                     CLUSTER_UNIVERSIDAD == "Others" ~ "#9B59B6",                # Púrpura
                     TRUE ~ "#2F2F2F"                                            # Gris muy oscuro
                   ), "; color: white; padding: 4px 8px; border-radius: 12px; font-size: 10px; font-weight: bold;'>", 
                   ifelse(is.na(CLUSTER_UNIVERSIDAD) | CLUSTER_UNIVERSIDAD == "", "No Cluster", CLUSTER_UNIVERSIDAD), "</span>",
                  "</div>",
                  "<div style='display: grid; grid-template-columns: 1fr 1fr; gap: 8px; margin-bottom: 10px;'>",
                  "<div style='background: #e8f5e8; padding: 8px; border-radius: 6px; border-left: 4px solid #27ae60;'>",
                  "<strong style='color: #27ae60; font-size: 11px;'>📚 UAI</strong><br>",
                  "<div style='font-size: 10px; margin-top: 4px;'>",
                  "<strong>Market Share:</strong> ", sprintf("%.1f%%", MARKET_SHARE_UAI_MATRI), "<br>",
                  "<strong>Enrolled:</strong> ", MATRICULADOS_UAI, "<br>",
                  "<strong>Applications:</strong> ", POSTULANTES_UAI,
                  "</div></div>",
                  "<div style='background: #fff3cd; padding: 8px; border-radius: 6px; border-left: 4px solid #f39c12;'>",
                  "<strong style='color: #f39c12; font-size: 11px;'>🏛️ COMP1</strong><br>",
                  "<div style='font-size: 10px; margin-top: 4px;'>",
                  "<strong>Market Share:</strong> ", sprintf("%.1f%%", MARKET_SHARE_COMP1_MATRI), "<br>",
                  "<strong>Enrolled:</strong> ", MATRI_COMPETENCIA1, "<br>",
                  "<strong>Applications:</strong> ", POST_COMPETENCIA1,
                  "</div></div>",
                  "<div style='background: #f8d7da; padding: 8px; border-radius: 6px; border-left: 4px solid #e74c3c;'>",
                  "<strong style='color: #e74c3c; font-size: 11px;'>🎓 COMP2</strong><br>",
                  "<div style='font-size: 10px; margin-top: 4px;'>",
                  "<strong>Market Share:</strong> ", sprintf("%.1f%%", MARKET_SHARE_COMP2_MATRI), "<br>",
                  "<strong>Enrolled:</strong> ", MATRI_COMPETENCIA2, "<br>",
                  "<strong>Applications:</strong> ", POST_COMPETENCIA2,
                  "</div></div>",
                  "<div style='background: #e3e3e3; padding: 8px; border-radius: 6px; border-left: 4px solid #7f8c8d;'>",
                  "<strong style='color: #7f8c8d; font-size: 11px;'>🏫 OTHERS</strong><br>",
                  "<div style='font-size: 10px; margin-top: 4px;'>",
                  "<strong>Market Share:</strong> ", sprintf("%.1f%%", MARKET_SHARE_OTHERS_MATRI), "<br>",
                  "<strong>Enrolled:</strong> ", MATRI_OTHERS, "<br>",
                  "<strong>Applications:</strong> ", POST_OTHERS,
                  "</div></div>",
                  "</div>",
                  "<div style='background: #f0f0f0; padding: 8px; border-radius: 4px; font-size: 11px;'>",
                  "<strong>Academic Profile:</strong> ", CLUSTER_NOMBRE, "<br>",
                  "<strong>Total Students:</strong> ", MATRICULADOS, " | <strong>Avg Score:</strong> ", {
                    score_str <- as.character(PTJE_PROM)
                    substr(score_str, 1, 3)
                  },
                  "</div>",
                  "</div>",
                  "</div>"),
    group = "Competitive Analysis"
  ) %>%
  
  # Add cluster visualization layer
  addCircleMarkers(
    data = datos_osm_clean,
    lng = ~LONGITUD, lat = ~LATITUD,
    color = ~case_when(
      CLUSTER_NOMBRE == "Engineer" ~ "#e74c3c",
      CLUSTER_NOMBRE == "Law" ~ "#f39c12",
      CLUSTER_NOMBRE == "Balanced" ~ "#2ecc71",
      CLUSTER_NOMBRE == "Journalism" ~ "#3498db",
      CLUSTER_NOMBRE == "Commercial" ~ "#9b59b6",
      CLUSTER_NOMBRE == "Psicology" ~ "#1abc9c",
      TRUE ~ "#95a5a6"
    ),
    stroke = FALSE, fillOpacity = 0.7,
    radius = 8,
    popup = ~paste("<div style='font-size: 12px; width: 320px;'>",
                   "<div style='background: linear-gradient(135deg, #667eea 0%, #764ba2 100%); color: white; padding: 10px; border-radius: 8px 8px 0 0; margin: -10px -10px 10px -10px;'>",
                   "<h3 style='margin: 0; font-size: 16px;'>", NOM_RBD, "</h3>",
                   "</div>",
                   "<div style='background: #f8f9fa; padding: 10px; border-radius: 0 0 8px 8px;'>",
                   "<div style='display: grid; grid-template-columns: 1fr 1fr 1fr; gap: 8px; margin-bottom: 10px;'>",
                   "<div style='background: #e8f5e8; padding: 8px; border-radius: 6px; border-left: 4px solid #27ae60;'>",
                   "<strong style='color: #27ae60; font-size: 11px;'>UAI</strong><br>",
                   "<div style='font-size: 10px; margin-top: 4px;'>",
                   "<strong>Market Share:</strong><br>", sprintf("%.1f%%", MARKET_SHARE_UAI_MATRI), "<br>",
                   "<strong>Enrolled:</strong><br>", MATRICULADOS_UAI, "<br>",
                   "<strong>Applications:</strong><br>", POSTULANTES_UAI, "<br>",
                   "<strong>Avg Score:</strong><br>", {
                     score_str <- as.character(PTJE_PROM)
                     # Show only first 3 digits for visualization
                     substr(score_str, 1, 3)
                   },
                   "</div></div>",
                   "<div style='background: #fff3cd; padding: 8px; border-radius: 6px; border-left: 4px solid #f39c12;'>",
                   "<strong style='color: #f39c12; font-size: 11px;'>COMP1</strong><br>",
                   "<div style='font-size: 10px; margin-top: 4px;'>",
                   "<strong>Market Share:</strong><br>", sprintf("%.1f%%", MARKET_SHARE_COMP1_MATRI), "<br>",
                   "<strong>Enrolled:</strong><br>", MATRI_COMPETENCIA_1, "<br>",
                   "<strong>Applications:</strong><br>", POSTULANTES_COMPETENCIA_1, "<br>",
                   "<strong>Lift vs UAI:</strong><br>", sprintf("%.2fx", LIFT_UAI_vs_COMP1), "<br>",
                   "<strong>Avg Score:</strong><br>", {
                     score_str <- as.character(PTJE_PROM)
                     # Show only first 3 digits for visualization
                     substr(score_str, 1, 3)
                   },
                   "</div></div>",
                   "<div style='background: #f8d7da; padding: 8px; border-radius: 6px; border-left: 4px solid #e74c3c;'>",
                   "<strong style='color: #e74c3c; font-size: 11px;'>COMP2</strong><br>",
                   "<div style='font-size: 10px; margin-top: 4px;'>",
                   "<strong>Market Share:</strong><br>", sprintf("%.1f%%", MARKET_SHARE_COMP2_MATRI), "<br>",
                   "<strong>Enrolled:</strong><br>", MATRI_COMPETENCIA_2, "<br>",
                   "<strong>Applications:</strong><br>", POSTULANTES_COMPETENCIA_2, "<br>",
                   "<strong>Lift vs UAI:</strong><br>", sprintf("%.2fx", LIFT_UAI_vs_COMP2), "<br>",
                   "<strong>Avg Score:</strong><br>", {
                     score_str <- as.character(PTJE_PROM)
                     # Show only first 3 digits for visualization
                     substr(score_str, 1, 3)
                   },
                   "</div></div>",
                   "<div style='background: #e3e3e3; padding: 8px; border-radius: 6px; border-left: 4px solid #7f8c8d;'>",
                   "<strong style='color: #7f8c8d; font-size: 11px;'>OTHERS</strong><br>",
                   "<div style='font-size: 10px; margin-top: 4px;'>",
                   "<strong>Market Share:</strong><br>", sprintf("%.1f%%", MARKET_SHARE_OTHERS_MATRI), "<br>",
                   "<strong>Enrolled:</strong><br>", MATRI_OTHERS, "<br>",
                   "<strong>Applications:</strong><br>", POST_OTHERS,
                   "</div></div>",
                   "</div>",
                   "<div style='background: #f0f0f0; padding: 8px; border-radius: 4px; font-size: 11px;'>",
                  "<strong>Career Cluster:</strong> ", CLUSTER_NOMBRE, "<br>",
                  "<strong>University Cluster:</strong> ", ifelse(is.na(CLUSTER_UNIVERSIDAD) | CLUSTER_UNIVERSIDAD == "", "N/A", CLUSTER_UNIVERSIDAD), "<br>",
                   "<strong>Total Students:</strong> ", MATRICULADOS,
                   "</div>",
                   "</div>",
                   "</div>"),
    group = "School Clusters"
  ) %>%
  
  # University markers removed - university clusters are now shown in school popups
  # Universities are represented through CLUSTER_UNIVERSIDAD column in school data
  
  # Add legends
  addLegend("bottomright", 
            colors = c("#FF0000", "#0000FF", "#00FF00", "#FF00FF", "#FFA500", "#9B59B6", "#2F2F2F"),
            labels = c("OTHERS_COMP1_LOW", "UAI", "COMP1", "COMP1_COMP2", "UAI2", "Others", "No Cluster"),
            title = "University Cluster", 
            opacity = 1, 
            group = "Competitive Analysis") %>%
  addLegend("bottomleft", 
            colors = c("#e74c3c", "#f39c12", "#2ecc71", "#3498db", "#9b59b6", "#1abc9c"),
            labels = c("Engineer", "Law", "Balanced", "Journalism", "Commercial", "Psicology"),
            title = "School Clusters", 
            opacity = 1, 
            group = "School Clusters") %>%
  
  # Add layer control
  addLayersControl(
    baseGroups = c("OpenStreetMap Standard", "OpenStreetMap DE", "OpenStreetMap France", "OpenStreetMap HOT",
                   "CartoDB Light", "CartoDB Dark", "Esri Street", "Satellite", "Stamen Toner", "Stamen Terrain"),
    overlayGroups = c("Competitive Analysis", "School Clusters"),
    options = layersControlOptions(collapsed = FALSE)
  ) %>%
  
  # Add custom search control and filter controls for CSV schools
  htmlwidgets::onRender(., "
    function(el, x) {
      var map = this;
      
      // SIMPLE FILTER SYSTEM - Works on all maps
      var allMarkers = [];
      var totalSlider = null;
      var title = null;
      var maxTotal = 500;
      
      // Simple function to get Total Students from popup HTML
      function getTotalStudents(marker) {
        if (!marker || !marker.options || !marker.options.popup) return 0;
        var popup = marker.options.popup;
        var str = typeof popup === 'string' ? popup : (popup.toString ? popup.toString() : '');
        if (!str) return 0;
        // Find Total Students: followed by a number
        var match = str.match(/Total Students[^:]*:\\s*([0-9,.]+)/);
        if (!match) match = str.match(/Total Students[^0-9]*([0-9,.]+)/);
        if (match && match[1]) {
          var num = parseInt(match[1].toString().replace(/,/g, '').split('.')[0]) || 0;
          return num;
        }
        return 0;
      }
      
      // Simple marker collection - just get all circle markers
      function collectAllMarkers() {
        allMarkers = [];
        map.eachLayer(function(layer) {
          if (layer instanceof L.CircleMarker && layer.options && layer.options.popup) {
            allMarkers.push(layer);
            layer._totalStudents = getTotalStudents(layer);
          }
          if (layer instanceof L.LayerGroup) {
            layer.eachLayer(function(subLayer) {
              if (subLayer instanceof L.CircleMarker && subLayer.options && subLayer.options.popup) {
                allMarkers.push(subLayer);
                subLayer._totalStudents = getTotalStudents(subLayer);
              }
            });
          }
        });
        // Calculate max
        maxTotal = 0;
        allMarkers.forEach(function(m) {
          if (m._totalStudents > maxTotal) maxTotal = m._totalStudents;
        });
        maxTotal = Math.min(maxTotal || 500, 500);
        console.log('Collected ' + allMarkers.length + ' markers, max total: ' + maxTotal);
      }
      
      // Simple filter - just show/hide based on value
      function applyFilter() {
        if (!totalSlider || allMarkers.length === 0) return;
        var minVal = parseInt(totalSlider.value) || 0;
        var visible = 0;
        
        allMarkers.forEach(function(marker) {
          var val = marker._totalStudents || getTotalStudents(marker);
          var isOnMap = map.hasLayer(marker);
          
          if (minVal === 0 || val >= minVal) {
            // Should be visible
            if (!isOnMap) {
              // Find the marker's layer group or add to map
              var groupName = marker.options ? marker.options.group : null;
              if (groupName) {
                map.eachLayer(function(layer) {
                  if (layer instanceof L.LayerGroup) {
                    layer.eachLayer(function(l) {
                      if (l instanceof L.CircleMarker && l.options && l.options.group === groupName) {
                        marker.addTo(layer);
                        return;
                      }
                    });
                  }
                });
              }
              if (!map.hasLayer(marker)) marker.addTo(map);
            }
            visible++;
          } else {
            // Should be hidden
            if (isOnMap) marker.remove();
          }
        });
        
        if (title) title.textContent = 'Total Students (' + visible + ' visible)';
        console.log('Filter applied: min=' + minVal + ', visible=' + visible);
      }
      
      // Create filter control
      var controlPanel = L.control({position: 'topright'});
      controlPanel.onAdd = function(map) {
        var div = L.DomUtil.create('div', 'filter-panel');
        div.style.cssText = 'background: white; padding: 15px; border-radius: 8px; box-shadow: 0 2px 10px rgba(0,0,0,0.3); min-width: 280px; z-index: 1000;';
        
        title = document.createElement('h4');
        title.textContent = 'Total Students';
        title.style.cssText = 'margin: 0 0 15px 0; font-size: 16px; color: #333;';
        div.appendChild(title);
        
        var label = document.createElement('label');
        label.textContent = 'Total Students (min):';
        label.style.cssText = 'display: block; margin-bottom: 5px; font-size: 12px; font-weight: bold; color: #555;';
        div.appendChild(label);
        
        totalSlider = document.createElement('input');
        totalSlider.type = 'range';
        totalSlider.min = '0';
        totalSlider.max = String(maxTotal);
        totalSlider.value = '0';
        totalSlider.step = '10';
        totalSlider.style.cssText = 'width: 100%; margin-bottom: 10px;';
        div.appendChild(totalSlider);
        
        var valueSpan = document.createElement('span');
        valueSpan.textContent = '0';
        valueSpan.style.cssText = 'display: block; text-align: center; font-size: 14px; font-weight: bold; color: #667eea; margin-bottom: 10px;';
        div.appendChild(valueSpan);
        
        totalSlider.addEventListener('input', function() {
          valueSpan.textContent = this.value;
          totalSlider.max = String(maxTotal); // Update max in case it changed
          applyFilter();
        });
        
        L.DomEvent.disableClickPropagation(div);
        L.DomEvent.disableScrollPropagation(div);
        return div;
      };
      map.addControl(controlPanel);
      
      // Collect markers and initialize
      setTimeout(function() {
        collectAllMarkers();
        if (totalSlider) {
          totalSlider.max = String(maxTotal);
          applyFilter();
        }
      }, 500);
      
      setTimeout(function() {
        collectAllMarkers();
        if (totalSlider) {
          totalSlider.max = String(maxTotal);
          applyFilter();
        }
      }, 2000);
      
      map.on('layeradd', function() {
        setTimeout(collectAllMarkers, 100);
      });
      
      // Compatibility function (calls simple filter)
      function applyFilters() {
        applyFilter();
      }
      
      // Create custom search control
      var searchControl = L.control({position: 'topleft'});
      
      searchControl.onAdd = function(map) {
        var div = L.DomUtil.create('div', 'custom-search-control');
        div.style.cssText = 'background: white; padding: 5px; border-radius: 5px; box-shadow: 0 1px 5px rgba(0,0,0,0.4);';
        
        var input = document.createElement('input');
        input.type = 'text';
        input.placeholder = 'Search schools by name...';
        input.style.cssText = 'width: 200px; padding: 5px; border: 1px solid #ccc; border-radius: 3px; font-size: 12px;';
        div.appendChild(input);
        
        L.DomEvent.disableClickPropagation(div);
        L.DomEvent.disableScrollPropagation(div);
        
        var schoolData = [];
        map.eachLayer(function(layer) {
          if (layer instanceof L.CircleMarker && layer.options.popup) {
            var popupContent = layer.options.popup;
            var schoolNameMatch = popupContent.match(/<h3[^>]*>([^<]+)<\\/h3>/);
            if (schoolNameMatch) {
              schoolData.push({
                name: schoolNameMatch[1],
                layer: layer,
                latlng: layer.getLatLng()
              });
            }
          }
        });
        
        input.addEventListener('input', function(e) {
          var query = e.target.value.toLowerCase();
          if (query.length >= 2) {
            var matches = schoolData.filter(function(school) {
              return school.name.toLowerCase().includes(query);
            });
            
            if (matches.length > 0) {
              var match = matches[0];
              map.setView(match.latlng, 15);
              match.layer.openPopup();
            }
          }
        });
        
        return div;
      };
      
      map.addControl(searchControl);
    }
  ") %>%
  
  # Add advanced controls
  addScaleBar(position = "bottomleft") %>%
  addMeasure(position = "topleft") %>%
  addFullscreenControl() %>%
  addEasyButton(easyButton(
    icon = "fa-crosshairs", title = "Locate Me",
    onClick = JS("function(btn, map){ map.locate({setView: true}); }")
  )) %>%
  
  # Set initial view
  setView(lng = -71.5, lat = -35.0, zoom = 5)

osm_comprehensive_map
```

### 3. Advanced OpenStreetMap Features - Heatmap Analysis

```{r Advanced_OSM_Features, message=FALSE, warning=FALSE}
# Create heatmap with 3 different views for UAI, COMP1, and COMP2
osm_heatmap_features <- leaflet() %>%
  # Add OpenStreetMap as primary base layer
  addProviderTiles(providers$OpenStreetMap, group = "OpenStreetMap") %>%
  addProviderTiles(providers$CartoDB.Positron, group = "CartoDB Light") %>%
  addProviderTiles(providers$Esri.WorldImagery, group = "Satellite") %>%
  
  # UAI Heatmap - Blue gradient
  addHeatmap(
    data = datos_osm_clean %>% filter(MATRI_UAI_ACTUAL > 0),
    lng = ~LONGITUD, lat = ~LATITUD,
    intensity = ~MATRI_UAI_ACTUAL,
    blur = 25, max = 0.1, radius = 20,
    gradient = c("transparent", "lightblue", "blue", "darkblue", "navy"),
    group = "UAI Heatmap"
  ) %>%
  
  # COMP1 Heatmap - Orange/Red gradient
  addHeatmap(
    data = datos_osm_clean %>% filter(MATRI_COMP1_ACTUAL > 0),
    lng = ~LONGITUD, lat = ~LATITUD,
    intensity = ~MATRI_COMP1_ACTUAL,
    blur = 25, max = 0.1, radius = 20,
    gradient = c("transparent", "lightyellow", "orange", "red", "darkred"),
    group = "COMP1 Heatmap"
  ) %>%
  
  # COMP2 Heatmap - Green gradient
  addHeatmap(
    data = datos_osm_clean %>% filter(MATRI_COMP2_ACTUAL > 0),
    lng = ~LONGITUD, lat = ~LATITUD,
    intensity = ~MATRI_COMP2_ACTUAL,
    blur = 25, max = 0.1, radius = 20,
    gradient = c("transparent", "lightgreen", "green", "darkgreen", "forestgreen"),
    group = "COMP2 Heatmap"
  ) %>%
  
  # OTHERS Heatmap - Grey gradient
  addHeatmap(
    data = datos_osm_clean %>% filter(MATRI_OTHERS_ACTUAL > 0),
    lng = ~LONGITUD, lat = ~LATITUD,
    intensity = ~MATRI_OTHERS_ACTUAL,
    blur = 25, max = 0.1, radius = 20,
    gradient = c("transparent", "lightgrey", "grey", "darkgrey", "#5a5a5a"),
    group = "OTHERS Heatmap"
  ) %>%
  
  # Add fixed university markers (always visible) - same as first map
  # UAI Group - Blue color (#0000FF)
  addCircleMarkers(
    lng = -70.518, lat = -33.486,  # UAI Santiago - Campus Peñalolén
    radius = 12,
    color = "#0000FF",
    fillColor = "#0000FF",
    fillOpacity = 1,
    weight = 3,
    stroke = TRUE,
    popup = "<div style='font-size: 14px; width: 250px;'><div style='background: linear-gradient(135deg, #0000FF 0%, #2980b9 100%); color: white; padding: 12px; border-radius: 8px;'><h3 style='margin: 0; font-size: 18px;'>🏛️ UAI</h3><p style='margin: 5px 0 0 0; font-size: 12px; opacity: 0.9;'>Universidad Adolfo Ibáñez<br>Campus Peñalolén</p></div></div>"
  ) %>%
  addCircleMarkers(
    lng = -71.554162, lat = -33.011707,  # UAI Viña del Mar
    radius = 12,
    color = "#0000FF",
    fillColor = "#0000FF",
    fillOpacity = 1,
    weight = 3,
    stroke = TRUE,
    popup = "<div style='font-size: 14px; width: 250px;'><div style='background: linear-gradient(135deg, #0000FF 0%, #2980b9 100%); color: white; padding: 12px; border-radius: 8px;'><h3 style='margin: 0; font-size: 18px;'>🏛️ UAI</h3><p style='margin: 5px 0 0 0; font-size: 12px; opacity: 0.9;'>Universidad Adolfo Ibáñez<br>Campus Viña del Mar</p></div></div>"
  ) %>%
  # COMP1 Group - Green color (#00FF00)
  addCircleMarkers(
    lng = -70.6406, lat = -33.4411,  # PUC
    radius = 12,
    color = "#00FF00",
    fillColor = "#00FF00",
    fillOpacity = 1,
    weight = 3,
    stroke = TRUE,
    popup = "<div style='font-size: 14px; width: 250px;'><div style='background: linear-gradient(135deg, #00FF00 0%, #27ae60 100%); color: white; padding: 12px; border-radius: 8px;'><h3 style='margin: 0; font-size: 18px;'>🏛️ COMP1</h3><p style='margin: 5px 0 0 0; font-size: 12px; opacity: 0.9;'>Pontificia Universidad Católica<br>Campus San Joaquín</p></div></div>",
  ) %>%
  addCircleMarkers(
    lng = -70.6633, lat = -33.4575,  # U. de Chile
    radius = 12,
    color = "#00FF00",
    fillColor = "#00FF00",
    fillOpacity = 1,
    weight = 3,
    stroke = TRUE,
    popup = "<div style='font-size: 14px; width: 250px;'><div style='background: linear-gradient(135deg, #00FF00 0%, #27ae60 100%); color: white; padding: 12px; border-radius: 8px;'><h3 style='margin: 0; font-size: 18px;'>🏛️ COMP1</h3><p style='margin: 5px 0 0 0; font-size: 12px; opacity: 0.9;'>Universidad de Chile<br>Campus Beauchef</p></div></div>",
  ) %>%
  addCircleMarkers(
    lng = -71.595, lat = -33.035,  # USM
    radius = 12,
    color = "#00FF00",
    fillColor = "#00FF00",
    fillOpacity = 1,
    weight = 3,
    stroke = TRUE,
    popup = "<div style='font-size: 14px; width: 250px;'><div style='background: linear-gradient(135deg, #00FF00 0%, #27ae60 100%); color: white; padding: 12px; border-radius: 8px;'><h3 style='margin: 0; font-size: 18px;'>🏛️ COMP1</h3><p style='margin: 5px 0 0 0; font-size: 12px; opacity: 0.9;'>Universidad Santa María<br>Valparaíso</p></div></div>",
  ) %>%
  addCircleMarkers(
    lng = -71.6056, lat = -33.0447,  # PUCV
    radius = 12,
    color = "#00FF00",
    fillColor = "#00FF00",
    fillOpacity = 1,
    weight = 3,
    stroke = TRUE,
    popup = "<div style='font-size: 14px; width: 250px;'><div style='background: linear-gradient(135deg, #00FF00 0%, #27ae60 100%); color: white; padding: 12px; border-radius: 8px;'><h3 style='margin: 0; font-size: 18px;'>🏛️ COMP1</h3><p style='margin: 5px 0 0 0; font-size: 12px; opacity: 0.9;'>Pontificia Universidad Católica de Valparaíso<br>Valparaíso</p></div></div>",
  ) %>%
  addCircleMarkers(
    lng = -70.682766, lat = -33.448942,  # USACH
    radius = 12,
    color = "#00FF00",
    fillColor = "#00FF00",
    fillOpacity = 1,
    weight = 3,
    stroke = TRUE,
    popup = "<div style='font-size: 14px; width: 250px;'><div style='background: linear-gradient(135deg, #00FF00 0%, #27ae60 100%); color: white; padding: 12px; border-radius: 8px;'><h3 style='margin: 0; font-size: 18px;'>🏛️ COMP1</h3><p style='margin: 5px 0 0 0; font-size: 12px; opacity: 0.9;'>Universidad de Santiago de Chile<br>Campus Santiago</p></div></div>",
  ) %>%
  # COMP2 Group - Magenta color (#FF00FF)
  addCircleMarkers(
    lng = -70.5011, lat = -33.3917,  # UDD
    radius = 12,
    color = "#FF00FF",
    fillColor = "#FF00FF",
    fillOpacity = 1,
    weight = 3,
    stroke = TRUE,
    popup = "<div style='font-size: 14px; width: 250px;'><div style='background: linear-gradient(135deg, #FF00FF 0%, #9b59b6 100%); color: white; padding: 12px; border-radius: 8px;'><h3 style='margin: 0; font-size: 18px;'>🏛️ COMP2</h3><p style='margin: 5px 0 0 0; font-size: 12px; opacity: 0.9;'>Universidad del Desarrollo<br>Campus Las Condes</p></div></div>",
  ) %>%
  addCircleMarkers(
    lng = -70.507468, lat = -33.404007,  # U. de los Andes
    radius = 12,
    color = "#FF00FF",
    fillColor = "#FF00FF",
    fillOpacity = 1,
    weight = 3,
    stroke = TRUE,
    popup = "<div style='font-size: 14px; width: 250px;'><div style='background: linear-gradient(135deg, #FF00FF 0%, #9b59b6 100%); color: white; padding: 12px; border-radius: 8px;'><h3 style='margin: 0; font-size: 18px;'>🏛️ COMP2</h3><p style='margin: 5px 0 0 0; font-size: 12px; opacity: 0.9;'>Universidad de los Andes<br>Campus San Carlos</p></div></div>",
  ) %>%
  addCircleMarkers(
    lng = -71.5423, lat = -33.0337,  # UNAB
    radius = 12,
    color = "#FF00FF",
    fillColor = "#FF00FF",
    fillOpacity = 1,
    weight = 3,
    stroke = TRUE,
    popup = "<div style='font-size: 14px; width: 250px;'><div style='background: linear-gradient(135deg, #FF00FF 0%, #9b59b6 100%); color: white; padding: 12px; border-radius: 8px;'><h3 style='margin: 0; font-size: 18px;'>🏛️ COMP2</h3><p style='margin: 5px 0 0 0; font-size: 12px; opacity: 0.9;'>Universidad Andrés Bello<br>Campus Viña del Mar</p></div></div>",
  ) %>%
  
  # Add circle markers to show individual schools
  addCircleMarkers(
    data = datos_osm_clean %>% filter(MATRI_UAI_ACTUAL > 0),
    lng = ~LONGITUD, lat = ~LATITUD,
    color = "#3498db", stroke = TRUE, weight = 2, fillOpacity = 0.8,
    radius = ~sqrt(MATRI_UAI_ACTUAL) * 2 + 5,
    popup = ~paste("<div style='font-size: 12px; width: 280px;'>",
                   "<div style='background: linear-gradient(135deg, #3498db 0%, #2980b9 100%); color: white; padding: 8px; border-radius: 6px 6px 0 0; margin: -10px -10px 8px -10px;'>",
                   "<h4 style='margin: 0; font-size: 14px;'>", NOM_RBD, "</h4>",
                   "</div>",
                  "<div style='background: #f8f9fa; padding: 8px; border-radius: 0 0 6px 6px;'>",
                  "<div style='display: grid; grid-template-columns: 1fr 1fr; gap: 6px; margin-bottom: 8px;'>",
                  "<div style='background: #e3f2fd; padding: 6px; border-radius: 4px; border-left: 3px solid #3498db;'>",
                  "<strong style='color: #2980b9; font-size: 10px;'>UAI</strong><br>",
                  "<div style='font-size: 9px; margin-top: 3px;'>",
                  "<strong>Market Share:</strong><br>", sprintf("%.1f%%", MARKET_SHARE_UAI_MATRI), "<br>",
                  "<strong>Enrolled:</strong><br>", MATRI_UAI_ACTUAL, "<br>",
                  "<strong>Applications:</strong><br>", POST_UAI_ACTUAL,
                  "</div></div>",
                  "<div style='background: #fff3e0; padding: 6px; border-radius: 4px; border-left: 3px solid #ff9800;'>",
                  "<strong style='color: #f57c00; font-size: 10px;'>COMP1</strong><br>",
                  "<div style='font-size: 9px; margin-top: 3px;'>",
                  "<strong>Market Share:</strong><br>", sprintf("%.1f%%", MARKET_SHARE_COMP1_MATRI), "<br>",
                  "<strong>Enrolled:</strong><br>", MATRI_COMP1_ACTUAL, "<br>",
                  "<strong>Applications:</strong><br>", POST_COMP1_ACTUAL,
                  "</div></div>",
                  "<div style='background: #e8f5e8; padding: 6px; border-radius: 4px; border-left: 3px solid #4caf50;'>",
                  "<strong style='color: #388e3c; font-size: 10px;'>COMP2</strong><br>",
                  "<div style='font-size: 9px; margin-top: 3px;'>",
                  "<strong>Market Share:</strong><br>", sprintf("%.1f%%", MARKET_SHARE_COMP2_MATRI), "<br>",
                  "<strong>Enrolled:</strong><br>", MATRI_COMP2_ACTUAL, "<br>",
                  "<strong>Applications:</strong><br>", POST_COMP2_ACTUAL,
                  "</div></div>",
                  "<div style='background: #e3e3e3; padding: 6px; border-radius: 4px; border-left: 3px solid #7f8c8d;'>",
                  "<strong style='color: #7f8c8d; font-size: 10px;'>🏫 OTHERS</strong><br>",
                  "<div style='font-size: 9px; margin-top: 3px;'>",
                  "<strong>Market Share:</strong><br>", sprintf("%.1f%%", MARKET_SHARE_OTHERS_MATRI), "<br>",
                  "<strong>Enrolled:</strong><br>", MATRI_OTHERS_ACTUAL, "<br>",
                  "<strong>Applications:</strong><br>", POST_OTHERS_ACTUAL,
                  "</div></div>",
                  "</div>",
                   "<div style='background: #f0f0f0; padding: 6px; border-radius: 4px; font-size: 10px;'>",
                   "<strong>Total Students:</strong> ", MATRICULADOS, " | <strong>Avg Score:</strong> ", sprintf("%.2f", round(as.numeric(gsub(",", ".", PTJE_PROM)) / 1000000000000, 2)) %>% gsub("\\.", ",", .),
                   "</div>",
                   "</div>",
                   "</div>"),
    group = "School Markers"
  ) %>%
  
  # Add legends for each heatmap
  addLegend("bottomright", 
            colors = c("navy", "darkblue", "blue", "lightblue", "transparent"),
            labels = c("High", "Medium-High", "Medium", "Low", "None"),
            title = "UAI Enrollment Intensity", 
            opacity = 1, 
            group = "UAI Heatmap") %>%
  
  addLegend("bottomleft", 
            colors = c("darkred", "red", "orange", "lightyellow", "transparent"),
            labels = c("High", "Medium-High", "Medium", "Low", "None"),
            title = "COMP1 Enrollment Intensity", 
            opacity = 1, 
            group = "COMP1 Heatmap") %>%
  
  addLegend("topright", 
            colors = c("forestgreen", "darkgreen", "green", "lightgreen", "transparent"),
            labels = c("High", "Medium-High", "Medium", "Low", "None"),
            title = "COMP2 Enrollment Intensity", 
            opacity = 1, 
            group = "COMP2 Heatmap") %>%
  
  addLegend("topleft", 
            colors = c("#5a5a5a", "darkgrey", "grey", "lightgrey", "transparent"),
            labels = c("High", "Medium-High", "Medium", "Low", "None"),
            title = "OTHERS Enrollment Intensity", 
            opacity = 1, 
            group = "OTHERS Heatmap") %>%
  
  # Add layer control
  addLayersControl(
    baseGroups = c("OpenStreetMap", "CartoDB Light", "Satellite"),
    overlayGroups = c("UAI Heatmap", "COMP1 Heatmap", "COMP2 Heatmap", "OTHERS Heatmap", "School Markers"),
    options = layersControlOptions(collapsed = FALSE)
  ) %>%
  
  # Add advanced controls
  addScaleBar(position = "bottomleft") %>%
  addMeasure(position = "topleft") %>%
  addFullscreenControl() %>%
  addEasyButton(easyButton(
    icon = "fa-home", title = "Reset View",
    onClick = JS("function(btn, map){ map.setView([-35.0, -71.5], 5); }")
  )) %>%
  
  # Set initial view
  setView(lng = -71.5, lat = -35.0, zoom = 5) %>%
  
  # Add custom search control and filter controls for CSV schools
  htmlwidgets::onRender(., "
    function(el, x) {
      var map = this;
      
      // SIMPLE FILTER SYSTEM - Works on all maps
      var allMarkers = [];
      var totalSlider = null;
      var title = null;
      var maxTotal = 500;
      
      // Simple function to get Total Students from popup HTML
      function getTotalStudents(marker) {
        if (!marker || !marker.options || !marker.options.popup) return 0;
        var popup = marker.options.popup;
        var str = typeof popup === 'string' ? popup : (popup.toString ? popup.toString() : '');
        if (!str) return 0;
        var match = str.match(/Total Students[^:]*:\\s*([0-9,.]+)/);
        if (!match) match = str.match(/Total Students[^0-9]*([0-9,.]+)/);
        if (match && match[1]) {
          var num = parseInt(match[1].toString().replace(/,/g, '').split('.')[0]) || 0;
          return num;
        }
        return 0;
      }
      
      // Simple marker collection
      function collectAllMarkers() {
        allMarkers = [];
        map.eachLayer(function(layer) {
          if (layer instanceof L.CircleMarker && layer.options && layer.options.popup) {
            allMarkers.push(layer);
            layer._totalStudents = getTotalStudents(layer);
          }
          if (layer instanceof L.LayerGroup) {
            layer.eachLayer(function(subLayer) {
              if (subLayer instanceof L.CircleMarker && subLayer.options && subLayer.options.popup) {
                allMarkers.push(subLayer);
                subLayer._totalStudents = getTotalStudents(subLayer);
              }
            });
          }
        });
        maxTotal = 0;
        allMarkers.forEach(function(m) {
          if (m._totalStudents > maxTotal) maxTotal = m._totalStudents;
        });
        maxTotal = Math.min(maxTotal || 500, 500);
      }
      
      // Simple filter
      function applyFilter() {
        if (!totalSlider || allMarkers.length === 0) return;
        var minVal = parseInt(totalSlider.value) || 0;
        var visible = 0;
        allMarkers.forEach(function(marker) {
          var val = marker._totalStudents || getTotalStudents(marker);
          var isOnMap = map.hasLayer(marker);
          if (minVal === 0 || val >= minVal) {
            if (!isOnMap) {
              var groupName = marker.options ? marker.options.group : null;
              if (groupName) {
                map.eachLayer(function(layer) {
                  if (layer instanceof L.LayerGroup) {
                    layer.eachLayer(function(l) {
                      if (l instanceof L.CircleMarker && l.options && l.options.group === groupName) {
                        marker.addTo(layer);
                        return;
                      }
                    });
                  }
                });
              }
              if (!map.hasLayer(marker)) marker.addTo(map);
            }
            visible++;
          } else {
            if (isOnMap) marker.remove();
          }
        });
        if (title) title.textContent = 'Total Students (' + visible + ' visible)';
      }
      
      // Create filter control
      var controlPanel = L.control({position: 'topright'});
      controlPanel.onAdd = function(map) {
        var div = L.DomUtil.create('div', 'filter-panel');
        div.style.cssText = 'background: white; padding: 15px; border-radius: 8px; box-shadow: 0 2px 10px rgba(0,0,0,0.3); min-width: 280px; z-index: 1000;';
        title = document.createElement('h4');
        title.textContent = 'Total Students';
        title.style.cssText = 'margin: 0 0 15px 0; font-size: 16px; color: #333;';
        div.appendChild(title);
        var label = document.createElement('label');
        label.textContent = 'Total Students (min):';
        label.style.cssText = 'display: block; margin-bottom: 5px; font-size: 12px; font-weight: bold; color: #555;';
        div.appendChild(label);
        totalSlider = document.createElement('input');
        totalSlider.type = 'range';
        totalSlider.min = '0';
        totalSlider.max = String(maxTotal);
        totalSlider.value = '0';
        totalSlider.step = '10';
        totalSlider.style.cssText = 'width: 100%; margin-bottom: 10px;';
        div.appendChild(totalSlider);
        var valueSpan = document.createElement('span');
        valueSpan.textContent = '0';
        valueSpan.style.cssText = 'display: block; text-align: center; font-size: 14px; font-weight: bold; color: #667eea; margin-bottom: 10px;';
        div.appendChild(valueSpan);
        totalSlider.addEventListener('input', function() {
          valueSpan.textContent = this.value;
          totalSlider.max = String(maxTotal);
          applyFilter();
        });
        L.DomEvent.disableClickPropagation(div);
        L.DomEvent.disableScrollPropagation(div);
        return div;
      };
      map.addControl(controlPanel);
      
      setTimeout(function() {
        collectAllMarkers();
        if (totalSlider) {
          totalSlider.max = String(maxTotal);
          applyFilter();
        }
      }, 500);
      setTimeout(function() {
        collectAllMarkers();
        if (totalSlider) {
          totalSlider.max = String(maxTotal);
          applyFilter();
        }
      }, 2000);
      map.on('layeradd', function() {
        setTimeout(collectAllMarkers, 100);
      });
      
      // Create custom search control
      var searchControl = L.control({position: 'topleft'});
      
      searchControl.onAdd = function(map) {
        var div = L.DomUtil.create('div', 'custom-search-control');
        div.style.cssText = 'background: white; padding: 5px; border-radius: 5px; box-shadow: 0 1px 5px rgba(0,0,0,0.4);';
        
        var input = document.createElement('input');
        input.type = 'text';
        input.placeholder = 'Search schools by name...';
        input.style.cssText = 'width: 200px; padding: 5px; border: 1px solid #ccc; border-radius: 3px; font-size: 12px;';
        div.appendChild(input);
        
        L.DomEvent.disableClickPropagation(div);
        L.DomEvent.disableScrollPropagation(div);
        
        // Get school data from markers
        var schoolData = [];
        map.eachLayer(function(layer) {
          if (layer instanceof L.CircleMarker && layer.options.popup) {
            var popupContent = layer.options.popup;
            var schoolNameMatch = popupContent.match(/<h4[^>]*>([^<]+)<\\/h4>/);
            if (schoolNameMatch) {
              schoolData.push({
                name: schoolNameMatch[1],
                layer: layer,
                latlng: layer.getLatLng()
              });
            }
          }
        });
        
        input.addEventListener('input', function(e) {
          var query = e.target.value.toLowerCase();
          if (query.length >= 2) {
            var matches = schoolData.filter(function(school) {
              return school.name.toLowerCase().includes(query);
            });
            
            if (matches.length > 0) {
              var match = matches[0];
              map.setView(match.latlng, 15);
              match.layer.openPopup();
            }
          }
        });
        
        return div;
      };
      
      map.addControl(searchControl);
    }
  ")

osm_heatmap_features
```

### Interactive Schools Table with Filters

```{r Schools_Table, message=FALSE, warning=FALSE, echo=FALSE}
# Prepare data for interactive table
# Use datos (original, unfiltered) and calculate needed columns
schools_table_data <- datos %>%
  mutate(
    # Calculate market share if not already calculated
    TOTAL_MARKET_MATRI = coalesce(as.numeric(MATRICULADOS_UAI), 0) + 
                         coalesce(as.numeric(MATRI_COMPETENCIA1), 0) + 
                         coalesce(as.numeric(MATRI_COMPETENCIA2), 0) + 
                         coalesce(as.numeric(MATRI_OTHERS), 0),
    MARKET_SHARE_UAI_MATRI = if_else(TOTAL_MARKET_MATRI > 0, 
                                     (coalesce(as.numeric(MATRICULADOS_UAI), 0) / TOTAL_MARKET_MATRI) * 100, 0),
    MARKET_SHARE_COMP1_MATRI = if_else(TOTAL_MARKET_MATRI > 0, 
                                       (coalesce(as.numeric(MATRI_COMPETENCIA1), 0) / TOTAL_MARKET_MATRI) * 100, 0),
    MARKET_SHARE_COMP2_MATRI = if_else(TOTAL_MARKET_MATRI > 0, 
                                       (coalesce(as.numeric(MATRI_COMPETENCIA2), 0) / TOTAL_MARKET_MATRI) * 100, 0),
    MARKET_SHARE_OTHERS_MATRI = if_else(TOTAL_MARKET_MATRI > 0, 
                                        (coalesce(as.numeric(MATRI_OTHERS), 0) / TOTAL_MARKET_MATRI) * 100, 0)
  ) %>%
  mutate(
    # Ensure CLUSTER_UNIVERSIDAD is preserved as character with full names
    CLUSTER_UNIVERSIDAD = as.character(CLUSTER_UNIVERSIDAD)
  ) %>%
  select(
    School = NOM_RBD,
    Region = REGION_RBD,
    Total_Students = MATRICULADOS,
    Average_Score = PTJE_PROM,
    Career_Cluster = CLUSTER_CARRERA,
    University_Cluster = CLUSTER_UNIVERSIDAD,
    Matriculated_UAI = MATRICULADOS_UAI,
    Matriculated_COMP1 = MATRI_COMPETENCIA1,
    Matriculated_COMP2 = MATRI_COMPETENCIA2,
    Matriculated_Others = MATRI_OTHERS,
    Market_Share_UAI = MARKET_SHARE_UAI_MATRI,
    Market_Share_COMP1 = MARKET_SHARE_COMP1_MATRI,
    Market_Share_COMP2 = MARKET_SHARE_COMP2_MATRI,
    Market_Share_Others = MARKET_SHARE_OTHERS_MATRI
  ) %>%
  mutate(
    Total_Students = as.numeric(Total_Students),
    Average_Score = as.numeric(Average_Score),
    Matriculated_UAI = as.numeric(Matriculated_UAI),
    Matriculated_COMP1 = as.numeric(Matriculated_COMP1),
    Matriculated_COMP2 = as.numeric(Matriculated_COMP2),
    Matriculated_Others = as.numeric(Matriculated_Others),
    Market_Share_UAI = as.numeric(Market_Share_UAI),
    Market_Share_COMP1 = as.numeric(Market_Share_COMP1),
    Market_Share_COMP2 = as.numeric(Market_Share_COMP2),
    Market_Share_Others = as.numeric(Market_Share_Others),
    Career_Cluster = ifelse(is.na(Career_Cluster) | Career_Cluster == "" | trimws(as.character(Career_Cluster)) == "", 
                           "Low_Volume", 
                           trimws(as.character(Career_Cluster))),
    # Preserve full cluster names exactly as they appear in CSV - no truncation
    # Replace empty values with "Low_Volume"
    # Ensure no leading/trailing spaces that could cause character loss
    University_Cluster = case_when(
      is.na(University_Cluster) ~ "Low_Volume",
      as.character(University_Cluster) == "" ~ "Low_Volume",
      trimws(as.character(University_Cluster)) == "" ~ "Low_Volume",
      TRUE ~ paste0(trimws(as.character(University_Cluster)))  # Ensure full name with no spaces
    ),
    Region = as.character(Region),
    # Replace NA with 0 for numeric columns to ensure filters work
    Total_Students = ifelse(is.na(Total_Students), 0, Total_Students),
    Average_Score = ifelse(is.na(Average_Score), 0, Average_Score),
    Matriculated_UAI = ifelse(is.na(Matriculated_UAI), 0, Matriculated_UAI),
    Matriculated_COMP1 = ifelse(is.na(Matriculated_COMP1), 0, Matriculated_COMP1),
    Matriculated_COMP2 = ifelse(is.na(Matriculated_COMP2), 0, Matriculated_COMP2),
    Matriculated_Others = ifelse(is.na(Matriculated_Others), 0, Matriculated_Others),
    Market_Share_UAI = ifelse(is.na(Market_Share_UAI), 0, Market_Share_UAI),
    Market_Share_COMP1 = ifelse(is.na(Market_Share_COMP1), 0, Market_Share_COMP1),
    Market_Share_COMP2 = ifelse(is.na(Market_Share_COMP2), 0, Market_Share_COMP2),
    Market_Share_Others = ifelse(is.na(Market_Share_Others), 0, Market_Share_Others)
  ) %>%
  arrange(School)

# Create interactive DataTable with improved numeric filtering
DT::datatable(
  schools_table_data,
  filter = "top",
  options = list(
    pageLength = 25,
    lengthMenu = c(10, 25, 50, 100, 200, 500, nrow(schools_table_data)),
    scrollX = TRUE,
    scrollY = "600px",
    autoWidth = FALSE,
    searchHighlight = TRUE,
    # Ensure all columns are searchable and filterable
    searchCols = NULL,
    columnDefs = list(
      list(width = "200px", targets = 0, searchable = TRUE),  # School name
      list(width = "100px", targets = 1, searchable = TRUE),  # Region
      list(width = "120px", targets = 2, searchable = TRUE, type = "num"),  # Total Students
      list(width = "120px", targets = 3, searchable = TRUE, type = "num"),  # Average Score
      list(width = "150px", targets = 4, searchable = TRUE),  # Career Cluster
      list(width = "220px", targets = 5, searchable = TRUE),  # University Cluster - wide for full names
      list(width = "120px", targets = c(6, 7, 8, 9), searchable = TRUE, type = "num"),  # Matriculated columns
      list(width = "130px", targets = c(10, 11, 12, 13), searchable = TRUE, type = "num"),  # Market Share columns
      list(className = "dt-center", targets = c(2, 3, 6, 7, 8, 9, 10, 11, 12, 13))  # Center numeric columns
    ),
    language = list(
      search = "Search all columns:",
      lengthMenu = "Show _MENU_ schools per page",
      info = "Showing _START_ to _END_ of _TOTAL_ schools",
      infoEmpty = "No schools found",
      infoFiltered = "(filtered from _MAX_ total schools)",
      zeroRecords = "No matching schools found"
    ),
    dom = "Bfrtip",
    buttons = list(
      list(extend = "copy", title = "Schools Data"),
      list(extend = "csv", title = "Schools Data", filename = "schools_data"),
      list(extend = "excel", title = "Schools Data", filename = "schools_data"),
      list(extend = "pdf", title = "Schools Data", filename = "schools_data"),
      list(extend = "print", title = "Schools Data")
    ),
    initComplete = DT::JS("
      function(settings, json) {
        var table = this.api();
        var numericColumns = [2, 3, 6, 7, 8, 9, 10, 11, 12, 13];
        var tableId = settings.nTable.id;
        
        numericColumns.forEach(function(colIdx) {
          var input = $(settings.nTHead).find('input').eq(colIdx);
          if (!input.length) return;
          
          input.attr('placeholder', 'Min value');
          
          input.off('keyup search input').on('keyup search input', function() {
            var val = this.value.trim();
            var searchId = 'minFilter_' + colIdx + '_' + tableId;
            
            $.fn.dataTable.ext.search = $.fn.dataTable.ext.search.filter(function(fn) {
              return !fn[searchId];
            });
            
            if (!val || val === '') {
              table.column(colIdx).search('', true, false).draw();
              return;
            }
            
            var minVal = parseFloat(val.replace(',', '.'));
            if (isNaN(minVal)) {
              table.column(colIdx).search(val, true, false).draw();
                        return;
            }
            
            var minFilter = function(settings, data, dataIndex) {
              if (!settings || !settings.nTable || !settings.nTable.id) return true;
              if (settings.nTable.id !== tableId) return true;
              var cellValue = parseFloat((data[colIdx] || '').toString().replace(/[^0-9.,-]/g, '').replace(',', '.')) || 0;
              return cellValue >= minVal;
            };
            
            minFilter[searchId] = true;
            $.fn.dataTable.ext.search.push(minFilter);
            table.draw();
          });
        });
      }
    ")
  ),
  extensions = c("Buttons", "Scroller", "FixedHeader"),
  rownames = FALSE,
  class = "display nowrap compact",
  style = "bootstrap4"
) %>%
  DT::formatRound(columns = c("Average_Score"), digits = 1) %>%
  DT::formatRound(columns = c("Total_Students", "Matriculated_UAI", "Matriculated_COMP1", 
                               "Matriculated_COMP2", "Matriculated_Others"), digits = 0) %>%
  DT::formatRound(columns = c("Market_Share_UAI", "Market_Share_COMP1", "Market_Share_COMP2", 
                               "Market_Share_Others"), digits = 2) %>%
  DT::formatStyle(
    columns = c("Career_Cluster", "University_Cluster"),
    backgroundColor = DT::styleEqual(
      levels = c("Engineer", "Law", "Balanced", "Journalism", "Commercial", "Psicology",
                 "UAI", "COMP1", "COMP2", "COMP1_COMP2", "UAI2", "Others", "OTHERS_COMP1_LOW", "Low_Volume"),
      values = c("#e74c3c", "#f39c12", "#2ecc71", "#3498db", "#9b59b6", "#1abc9c",
                 "#0000FF", "#00FF00", "#FF00FF", "#FF00FF", "#FFA500", "#9B59B6", "#FF0000", "#95a5a6")
    ),
    color = "white",
    fontWeight = "bold"
  )
```

**Table Features:**
- **Search**: Use the search box at top right to search across all columns
- **Column Filters**: 
  - **Region, Career Cluster, University Cluster**: Type text to filter by specific values
  - **Numeric columns** (Total Students, Average Score, Matriculated, Market Share): Type a number to show only rows where that column is **greater than or equal** to your value (minimum filter)
- **Sorting**: Click column headers to sort ascending/descending
- **Pagination**: Navigate through pages using controls at bottom
- **Export**: Use buttons to export data to CSV, Excel, PDF, or print
- **Scroll**: Scroll horizontally and vertically to see all columns
```
